Duration Analysis for Performing-Articulation performances

### 2020-05-19 material/analysis/expression/stim_a/ioi_duration.Rmd
update layout
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Analysis for Performing-Articulation performances (DURATION)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

duration_seq_stim_n <- fread("../../stim_n/seq.csv", header = T, sep = ",", dec = ".")
duration_seq_stim_n$SubNr <- factor(duration_seq_stim_n$SubNr)
duration_seq_stim_n$TrialNr <- factor(duration_seq_stim_n$TrialNr)
duration_seq_stim_n$TrialNr <- "Practice"

duration_seq <- rbind(duration_seq, duration_seq_stim_n)

@@

#### Distribution plot
#### Legato
```{r duration_dis_leg, fig.width = 12, echo = FALSE}
p_duration_dis_leg <- ggplot(dt_duration[Subcomponent == "Legato"], aes(x = normDu)) +
  geom_histogram(binwidth = .1, alpha=.5, position="identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised Duration", y = "Count", subtitle = "Duration: Performing-Articulation(Legato)")
p_duration_dis_leg
```

@@

### Exclude outlier participants
#### Legato
```{r outlier_leg, echo = FALSE}
# for legato
excluded_duration_leg <- duration[Subcomponent == "Legato" & Mean < duration_all[Subcomponent == "Legato"]$Mean+3*duration_all[Subcomponent == "Legato"]$SD & Mean > duration_all[Subcomponent == "Legato"]$Mean-3*duration_all$SD]
print(excluded_duration_leg)
```

#### Staccato
```{r outlier_sta, echo = FALSE}
# for staccato
excluded_duration_sta <- duration[Subcomponent == "Staccato" & Mean < duration_all[Subcomponent == "Staccato"]$Mean+3*duration_all[Subcomponent == "Staccato"]$SD & Mean > duration_all$Mean-3*duration_all[Subcomponent == "Staccato"]$SD]
print(excluded_duration_sta)
```

>>>>

---
title: 'Duration Analysis for Performing-Articulation performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

@@

### Distribution plot
#### Legato
```{r duration_dis_leg, fig.width = 12, echo = FALSE}
p_duration_dis_leg <- ggplot(dt_duration[Subcomponent == "Legato"], aes(x = normDu)) +
  geom_histogram(binwidth = .1, alpha=.5, position="identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised Duration", y = "Count", subtitle = "Duration: Performing-Articulation(Legato)")
p_duration_dis_leg
```

@@

### Valid performances (exclude outliers)
#### Legato
```{r outlier_leg, echo = FALSE}
# for legato
excluded_duration_leg <- duration[Subcomponent == "Legato" & Mean < duration_all[Subcomponent == "Legato"]$Mean+3*duration_all[Subcomponent == "Legato"]$SD & Mean > duration_all[Subcomponent == "Legato"]$Mean-3*duration_all$SD]
print(excluded_duration_leg)
```
- The number of excluded performance: `r duration_all[Subcomponent == "Legato"]$N-nrow(excluded_duration_leg)`

#### Staccato
```{r outlier_sta, echo = FALSE}
# for staccato
excluded_duration_sta <- duration[Subcomponent == "Staccato" & Mean < duration_all[Subcomponent == "Staccato"]$Mean+3*duration_all[Subcomponent == "Staccato"]$SD & Mean > duration_all$Mean-3*duration_all[Subcomponent == "Staccato"]$SD]
print(excluded_duration_sta)
```
- The number of excluded performance: `r duration_all[Subcomponent == "Staccato"]$N-nrow(excluded_duration_sta)`

```{r export, include = FALSE}
duration_valid <- dt_duration[, .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr)]
fwrite(duration_valid, "./duration_valid.csv")
```
